---
title: "Course Project - Shiny Application and Reproducible Pitch"
author: "fred"
date: "`r Sys.Date()`"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Pitch

The Shiny application developed for the week 4 assignment "Shiny Application and Reproducible Pitch" proposes a data vizualization of the Diamonds dataset distribution as well as linear models to model the relationship between carat and price.

The Shiny application gives the ability to the user to set the size of the random sample used to model this relationship. 

The Shiny appliation can be found here

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Diamond Price vs Carat
```{r diamonds, eval = TRUE, echo = FALSE}
# https://ggplot2.tidyverse.org/reference/diamonds.html
# https://bookdown.org/yih_huynh/Guide-to-R-Book/diamonds.html
#need to bucket
py <- plot_ly(diamonds, x = ~carat, y = ~price, type = "scatter", mode = 'markers', color = ~factor(cut))
py
```

## Thank you !
